A matrix-free approach for finite-strain hyperelastic problems using geometric multigrid

### 2018-10-23 doc/large_strain.tex
Add further funding acknowledgement for PS

P.~Steinmann acknowledges the support of the Cluster of Excellence Engineering of Advanced Materials (EAM) which made this collaboration possible.

>>>>

P.~Steinmann acknowledges the support of the Cluster of Excellence Engineering of Advanced Materials (EAM) which made this collaboration possible, as well as funding by the EPSRC Strategic Support Package ``Engineering of Active Materials by Multiscale/Multiphysics Computational Mechanics''.
